VAR Demonstration
=================

Two packages are very useful for VAR in R, MSBVAR and vars.  First load the MSBVAR package, and we will continue using the same data.

```
library(MSBVAR)
data(BCFData)
```

##vars package

Next load the vars library. Note that this overwrites the irf function in MSBVAR, we will deal with this later.

```{r}
library(vars)
```

We can plot the series again.

```{r}
#plot
plot(Y)
```

If we know we want to do a VAR analysis, with these three series, then we still need to know p, the lag length to use. We can check different specifications using this command:

```{r}
#lag specification
VARselect(Y, lag.max=15, type="const")
```

Make sure you understand the output. The AIC and BIC are most useful criterion to think about.

Once we have a lag length -- 3 is a reasonable and conservative choice here for now-- we want to estimate the reduced form VAR. 

```{r}
#estimate reduced form

rf.var0<-VAR(Y, p=3, type="const")

summary(rf.var0)
```

We can get a nice plot of this object with:

```{r}
plot(rf.var0)
```


The coefficients are not of obvious interest, but the impulse response functions are.

```{r}
#IRFs
irf(rf.var0, ortho= TRUE, boot=TRUE, ci=.95, runs=250, cumulative=FALSE) %>% plot()
```

It is importat to note that the confidence intervals are bootstapped here and need more samples.

Can also do residual diagnostic tests quickly.

```{r}
#Normality test
normality.test(rf.var0)

#Serial correlation
serial.test(rf.var0)
```

##MSBVAR package

Can do similar things in the MSBVAR package, but it also extends to a greater set of models.

In MSBVAR, lag selection is done by:

```{r}
#lag specification
var.lag.specification(Y, lagmax=15)


var.lag.specification(Y, lagmax=8)


var.lag.specification(Y, lagmax=6)
```

A reduced form, frequentist VAR is done by:

```{r}
#Reduced form frequentist VAR

rf.var1 <- reduced.form.var(Y, p=3)
```

We can access the coefficients and vcov matrix by:

```{r}
#where are coefs?

#intercepts?
rf.var1$intercept

#ars?
rf.var1$ar.coef

#Betahats?
rf.var1$Bhat

#vcov
rf.var1$vcv
```

Can also get a summary:

```{r}
#summmary
summary(rf.var1)
```

We can plot irfs, using the MSBVAR irf function (need to look in MSBVAR namespace):

```{r}
#Check IRFs?, use MSBVAR irf function (vars has one too, same name!)
MSBVAR::irf(rf.var1, nsteps=12) %>% plot()
```

Can change confidence intervals:

```{r}
#Try
mc.irf(rf.var1, draws=5000, nsteps=12) %>% plot(, probs=c(.05,.95))
```

Can you interpret this?







